%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Zachary}{Weeden}{ 3 Schell Pl. Rochester, NY 14608 \\
\href{mailto:zdw7287@rit.edu}{zdw7287@rit.edu} | 978.424.1345}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.32\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Rochester Institute}\subsection{of Technology}
\descript{BS in Computer Engineering Technology}
\location{Expected May 2018 | Rochester, NY \\ Accolades: Dean's List Spring 2016}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Personal Website: \href{https://people.rit.edu/zdw7287}{\custombold{https://people.rit.edu/zdw7287}} \\
Github: \\ \href{https://github.com/zweed4u}{\custombold{https://github.com/zweed4u}} \\
LinkedIn:\\  \href{https://www.linkedin.com/in/zweeden}{\custombold{https://www.linkedin.com/in/zweeden}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
DC/AC Circuits \textbullet{} Electronics I \& II \\
Microcontroller Systems \\
O-O Programming \textbullet{} Data Strcutures \\
Computational Problem Solving \\
Computer Science Theory \\
Digital Fundamentals \& System Design\\
Networking Technologies\\
Digital Signal Processing\\
Hardware Description Language\\
Embedded Systems Design
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Python \textbullet{} Bash \textbullet{} JavaScript \textbullet{} C \textbullet{} C++ \\
PHP \textbullet{} VHDL \textbullet{} Perl \textbullet{} \LaTeX\ \textbullet{} HTML 
\sectionsep

\subsection{Software}
Eclipse \textbullet{} Visual Studio \textbullet{} PyCharm \\ IDLE \textbullet{} Microsoft Office (72 WPM) \\ notePad++ \textbullet{} Sublime \textbullet{} Vi/Vim \\ Selenium \textbullet{} openQa \textbullet{} Altera Quartus II \\ QSYS \textbullet{} ModelSim \textbullet{} MultiSim \textbullet{} MiniTab \\ Linux/Windows/Mac OS \textbullet{} Git \\ Unix Tools \& Scripting
\sectionsep

\subsection{Equipment}
Digital Multimeter \textbullet{} Oscilloscope \\ 
Cyclone FPGA \textbullet{} Function Generator \\ Soldering \textbullet{} Protoboard \textbullet{} Arduino Uno \\ Raspberry Pi 
\sectionsep

\subsection{Extracurriculars}
2011 Varsity Baseball \textbullet{} RIT Tigers Men's Intercollegiate Varsity Baseball Team 
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.67\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{\href{http://www.datto.com/}{Datto Inc.}}
\descript{| Software Quality Assurance Intern \\ Automation Infrastructure }
\location{May 2016 – Dec 2016 (8 months) | Norwalk, CT \& Rochester, NY}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Manually tested front end and functionality of SaaS product
\item Wrote automated smoke tests in perl using openQA
%\item Updated deprecated git web project to support puppet integration for DLAMPs
\item Wrote code used to reset database instances that was integrated in framework 
\item Contributed to testing framework by wrapping API endpoints and SSH calls
\item Wrote automated regression tests for core products using testing framework
%\item Wrapped API endpoints in framework that were used in automated tests 
\item Wrote validity tests for each endpoint to ensure proper jsonrpc response
\item Completed tasks within sprints using agile development methods
\end{tightemize}
\sectionsep

\runsubsection{Self-Employed}
\descript{| Reseller}
\location{Sept 2011 – Present | Rochester, NY \& Middleton, MA}
\begin{tightemize}
\item Automate online retailers’ checkout process to
ensure purchase of limited sneakers which are then sold for profit on eBay
\item Methods include webcrawling, network activity analysis and use of various APIs
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{QA Git Web Tool}
\descript{| Datto Inc. Intern}
\location{Aug 2016 – Sept 2016 | Norwalk, CT \& Rochester, NY}
Deployed on a DLAMP device, a PHP webpage would allow a user to specify a repository and PR number to update or reset to master. A web handler would then validate the selection and resolve the proper path of the project and pass parameters to a shell script. The shell script would then make the git command to pull the selected version of the repository onto the device and install the project for further use.
\sectionsep

\runsubsection{Email Notifier}
\descript{| Datto Inc. Intern}
\location{June 2016 | Norwalk, CT}
Using a Raspberry Pi, a third party led beacon and a python script, the filtered folder
of an inbox was monitored for new, unread emails. On detection of a new message a
signal was sent to a designated pin on the Raspberry Pi and fed through an active low
relay which turned on the led. A second filtered folder was monitored for disabling
the led. The sender and time of this ”All Clear” email was logged.
\sectionsep

\runsubsection{\href{https://github.com/zweed4u/XML-Heartbeat}{Sitemap Page Monitor}}
\descript{| Personal}
\location{Sept 2015 – Present | Rochester, NY}
Polling sitemaps allowed for discovery of newly added pages which were then tweeted via a Twitter API wrapper.
Added pages' jsons are then
parsed for further information.
Exclusively used on webshops
that use the Shopify eCommerce platform.
\sectionsep

%\runsubsection{\href{https://github.com/zweed4u/Supreme}{Supreme1059}}
%\descript{| Personal}
%\location{March 2016 | Rochester, NY \& Middleton, MA}
%Polling of a mobile app endpoint allowed for quicker discovery of new products. Subsequent json pages are parsed and matched with user defined constraints such as size and colorway to generate a proper payload for an add to cart \& checkout request.
%\sectionsep

\runsubsection{\href{https://github.com/zweed4u/snapSave}{SnapSave}}
\descript{| Personal}
\location{May 2015 – Present | Rochester, NY \& Norwalk, CT \& Middleton, MA}
With the aid of an SSL kill switch and mitmproxy, SnapSave allows for the viewing and
downloading of a snap on a users desktop without voiding the expiration of the post
or notifying the sender that their post has been viewed.
\sectionsep

\runsubsection{\href{https://github.com/zweed4u/SNKRS}{5nkr5}}
\descript{| Personal}
\location{May 2015 – Present | Rochester, NY}
Reverse engineering of the SNKRS iOS app distributed by Nike with a mitmproxy
allowed for use of mobile app exclusive API endpoints for desktop users. Detailed
product information was also able to be gathered from various endpoints. Crucial in
that purchases on the app were given precendece over desktop purchases.
\sectionsep
\end{minipage} 
\end{document}  \documentclass[]{article}